---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

```{R, include = FALSE}

library(classdata)
library(tidyverse)
#Making sure to have the 0 as NA for feasibility purposes
ames[ames == 0] <- NA

```


## Step 1: Inspect the first few lines of the data set:


**What variables are there?**
```{R}
names(ames)
```

**Of what type are the variables?**
```{R}
sapply(ames, class)
```
**What does each variable mean?**

*Address = the address of the house, Style = the type of building, Occupancy = how many people live in the place, Sale Date = the date of the sale of the place, Sale Price = how much the place sold for, Multi Sale =  yes or no question, Year Built = The year the place had been built, Acres = how many acres the property is, Total Living Area = the square footage of the property, Bedrooms = amount of bedrooms in the property, Finished Basement Area = how much square footage of finished basement in the property, Lot area = square footage of the lot, AC = yes or no if the property has AC, Fireplace = yes or no if the property has a fireplace, Neighborhood = What place of Ames the property is located.*

**What do we expect their data range to be?**
```{R}

summary(ames, na.rm = FALSE)

```

## Step 2

**Is there a variable of special interest or focus?**

*Sale Price is the variable of interest*

## Step 3

**Start the exploration with the main variable**

```{r}
ggplot(ames, aes(x = `Sale Price`)) + 
  geom_histogram(bins = 500) +
  ggtitle("Sale Price")
```

**What is the range of the variable?**

*Range = 20500000*

**What is the general pattern?**

*The graph is right-skewed with extreme outliers*

**Is there anything odd?**

*No*

## Step 4

**For Each member to individually**

1. *What is the range of that variable*
2. *Plot. describe the pattern*
3. *What is the relationship to the main variable*
4. *Plot a scatterplot, boxplot or facetted barcharts (dependening on the types of variables involved)*
5. *Describe overall pattern, does this variable describe any oddities discovered in ?*
6. *Identify/follow-up on any oddities*


```{r}
## 4) Range = 13870
library(ggplot2)
ggplot(data = ames, aes(x = Style, fill = Style)) +
  geom_bar() +
  coord_flip()
  labs(title = "Bar Chart of Style",
       x = "Style",
       y = "Count")



```

```{r}
ggplot(ames, aes(x = Bedrooms)) + geom_histogram(binwidth = 1)
```

### Aidan

*Variable of interest : Year Built*

```{R}

ggplot(ames, aes(x=YearBuilt), na.rm = FALSE)+
  geom_histogram(binwidth = 1)

```

1. *What is the range of that variable*

  -1880 to 2020
  
2. *Plot. describe the pattern*

  -The graph is skewed left with no major outliers
  
3. *What is the relationship to the main variable*

```{R}
ggplot(ames, aes(x = YearBuilt, y=`Sale Price`), na.rm = FALSE)+
  geom_point()
```

 With only using sale price and year built to create a scatter plot there appears to be no correlation between the two variables.
 
  
4. *Plot a scatterplot, boxplot or facetted barcharts (dependening on the types of variables involved)*
  
```{R}
ggplot(ames, aes(x = YearBuilt, y=`Sale Price`), na.rm = FALSE)+
  geom_point()+
  facet_wrap(ames$Style, scales = 'free')
```
 
  
5. *Describe overall pattern, does this variable describe any oddities discovered in 3*

  -Following the visual of step 3, I had decided to add in a facet wrap of style to see if any relationships would show up between the three variables. I found the relationship between year built and sale price is dependent also on the style of the building. Though this relationship is also very weak and not a supper high r value.
  
 
### Luke

*Variable of interest : Neighborhood*

```{R}

ggplot(ames, aes(x = Neighborhood, color = Neighborhood), na.rm = FALSE) +
  geom_bar(show.legend = FALSE) +
  coord_flip()

```

1. *What is the range of that variable*

  -No range, since this is not a continuous variable
  
2. *Plot. describe the pattern*

  -Skewed right, but largely no dicernable pattern.
  
3. *What is the relationship to the main variable*

```{R}
neighbor_avg <- ames %>% group_by(Neighborhood) %>% 
  summarise(avg_neighbor = mean(`Sale Price`, na.rm = TRUE))

ggplot(neighbor_avg, aes(x = Neighborhood, y = avg_neighbor, color = Neighborhood)) +
  geom_col(show.legend = FALSE) +
  coord_flip()

```

```{R, echo=FALSE}
neighbor_avg2 <- neighbor_avg[-41, ]
neighbor_avg2 <- neighbor_avg2[-1, ]
  
ggplot(neighbor_avg2, aes(x = Neighborhood, y = avg_neighbor, color = Neighborhood)) +
  geom_col(show.legend = FALSE) +
  coord_flip()
```

There are clearly differences in the average price of a house depending on the the neighborhood it is located in, aas shown above.

4. *Plot a scatterplot, boxplot or facetted barcharts (depending on the types of variables involved)*
  
```{R}
ggplot(ames, aes(x = Neighborhood, y = YearBuilt, color = `Sale Price`), na.rm = FALSE)+
  geom_point() +
  coord_flip()

```
  
5. *Describe overall pattern, does this variable describe any oddities discovered in 3*

  -Following the visual of step 3, I decided to do try and see if the building's age correlated with either variable. While there is a clear correlation between many neighborhoods and the years the houses were built, with the exception of Investor owned it is hard to see a correlation between the two. I would need to strike the investor properties to be able to distinguish between the two. 
  


