---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

```{R, include = FALSE}

library(classdata)
library(tidyverse)

```


# Step 1: Inspect the first few lines of the data set:


**What variables are there?**
```{R}
names(ames)
```

**Of what type are the variables?**
```{R}
sapply(ames, class)
```
**What does each variable mean?**

*Address = the adress of the house, Style = the type of building, Occupancy = how many people live in the place, Sale Date = the date of the sale of the place, Sale Price = how much the place sold for, Multi Sale =  yes or no question, Year Built = The year the place had been built, Acres = how many acres the property is, Total Living Area = the square footage of the property, Bedrooms = amount of bedrooms in the property, Finished Basement Area = how much squarefootage of finished basement in the property, Lot area = square footage of the lot, AC = yes or no if the property has AC, Fireplace = yes or no if the property has a fireplace, Neighborhood = What place of Ames the property is located.*

**What do we expect their data range to be?**
```{R}
ames[ames == 0] <- NA
summary(ames)

```

# Step 2

**Is there a variable of special interest or focus?**

*Sale Price is the variable of interest*

# Step 3

**Start the exploration with the main variable**

```{r}
ggplot(ames, aes(x = `Sale Price`)) + 
  geom_histogram(bins = 500) +
  ggtitle("Sale Price")
```

**What is the range of the variable?**

*Range = 20500000*

**What is the general pattern?**

*The graph is right-skewed with extreme outliers*

**Is there anything odd?**

*Other than the outliers no*

# Step 4, Individual

```{r}
## 4) Range = 13870
library(ggplot2)
ggplot(data = ames, aes(x = Style, fill = Style)) +
  geom_bar() +
  coord_flip()
  labs(title = "Bar Chart of Style",
       x = "Style",
       y = "Count")



```

```{r}
ggplot(ames, aes(x = Bedrooms)) + geom_histogram(binwidth = 1)
```


